landlord

### 2022-10-26 src/landlord.Rmd
landlord catagory scores calculated
Update landlord.Rmd
test-from VA github desktop2
virginia new laptop github test
testing github token on new laptop
still testing github
wends AM

```{r}
# #only take Y/N columns
# MSA_landlord_data_binary <- MSA_landlord_data %>% 
#   select(cbsa, MSA, rent_control, eviction_notice_days, security_depopsit_limit_YN, notice_for_entry_days_YN)
```

```{r}
#mutate Y/N columns into 0/1

#rent_control
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    rent_control_binary = case_when(
      rent_control == "N" ~ 1, 
      rent_control == "Y" ~ 0))

#security_deposit_limit
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    security_depopsit_limit_binary = case_when(
      security_depopsit_limit_YN == "N" ~ 1, 
      security_depopsit_limit_YN == "Y" ~ 0))

#notice_of_entry_days
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    notice_for_entry_days_binary = case_when(
      notice_for_entry_days_YN == "N" ~ 1, 
      notice_for_entry_days_YN == "Y" ~ 0))
```

@@

>>>>

```{r}
# #rent_control
# MSA_landlord_data <- MSA_landlord_data %>% 
#   mutate(
#     rent_control_binary = case_when(
#       rent_control == "N" ~ 1, 
#       rent_control == "Y" ~ 0))

#security_deposit_limit
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    security_depopsit_limit_num = case_when(
      security_deposit_limit == "N" ~ 1.0, 
      security_deposit_limit == "1_month_rent" ~ 0.5,
      security_deposit_limit == "2_months_rent" ~ 0.0))

#notice_of_entry_days
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    notice_for_entry_days_num = case_when(
      notice_for_entry_days == "N" ~ 1.0, 
      notice_for_entry_days == "0" ~ 1.0,
      notice_for_entry_days == "0.5" ~ 0.75,
      notice_for_entry_days == "1" ~ 0.5,
      notice_for_entry_days == "2" ~ 0.0,))
```

@@

```{r}
#test Virginia new laptop on github
#testing github token setupf
```
